---
title: "Art from Art"
author: "Katherine"
date: '2023-01-28'
draft: false
slug: art-from-art
categories: []
tags: [art, tidytuesday]
---

I was really excited to see that the [Tidy Tuesday](https://github.com/rfordatascience/tidytuesday) for last week (1/17) was on Art! I haven't found a lot of great art data sets, and definitely not a lot with numerical data, so I was pretty interested in taking this data for a spin. The data is from the package [arthistory](https://saralemus7.github.io/arthistory/), and was originally collected as part of an undergraduate thesis on demographic representation in Art History textbooks. I decided that rather than analyzing the set of data, I was more interested in how the data could be used to produce generative art. With that goal in mind, I dug into exploring the data.

## Libraries and all that jazz

```{r}
#| title: libraries
#| output: false

# install.packages("arthistory")
library(arthistory)

# install.packages("MetBrewer")

# Art themed art must be art colored
library(MetBrewer)

# essentially my utilities 
library(tidyverse)
library(here)
library(glue)
```

```{r}
#| title: seed
# setting the all important seed
set.seed(9902)
# from https://www.calculatorsoup.com/calculators/statistics/random-number-generator.php
# range 1 - 10,000
```

## Initial Exploration

```{r}
#| title: initials

glimpse(worksjanson)

```

I was interested in using medium as the color for my art, however, it looks like there are a lot of different mediums listed, let's take a look at all of them:

```{r}
#| title: mediums
worksjanson |> 
  select(medium) |> 
  group_by(medium) |> 
  summarize(count = n()) |> 
  arrange(-count)
  
```

hi hi moo
